\section{Symmetry Breaking Weak Interactions}
\subsection{Key Questions About CP-Violation}   
\begin{itemize}
    \item Is the $CP$-violation in the $K^{0}$ system due to mixing or direct violation?
    \item \textbf{Mixing:} The $K^{0}_{S}$ and $K^{0}_{L}$ are non-orthogonal mixtures of $CP$-eigenstates. 
    \begin{equation}
      \ket{K^{0}_{S}, 0} = \frac{1}{\sqrt{1 + \left|ϵ\right|^2}} \left(\ket{K_1^{0}, 0} + \ket{K_2^{0}, 0}\right)
    \end{equation}
    \begin{equation}
        \ket{K^{0}_{L}, 0} = \frac{1}{\sqrt{1 + \left|ϵ\right|^2}} \left(ϵ\ket{K_1^{0}, 0} - \ket{K_2^{0}, 0}\right)
    \end{equation}
    \textbf{Direct:} The $K^{0}_{S}$ and $K^{0}_{L}$ are pure $CP$-eigenstates. Decaying to forbidden $CP$-states. 
    \begin{equation}
        \ket{K^{0}_{S}, 0} = \ket{K_1^{0}, 0}
    \end{equation}
    \begin{equation}
        \ket{K^{0}_{L}, 0} = \ket{K_2^{0}, 0}
    \end{equation} 
    \item \textbf{Conclusion:} There is both mixing and direct violation. The mixing is the dominant part. 
\end{itemize}













\subsubsection{CPT Invariance}
\begin{itemize}
    \item Predicted to be conserved in quantum field theory. If you break $CP$, you must also break $T$, meaning time. 
    \item This predicts the mass of particles and anti-particles should be the same. 
    \item There is yet to be found an exception to $CPT$-invariance. 
\end{itemize}


\subsection{CP and Flavour Oscillations in B-Decays}
\begin{itemize}
    \item Direct $CP$-violation plays a much larger role in $B$-decays than in $K$-decays.
    \item We have mixing, direct breaking, and interference. 
    \item We see this in both charged and neutral $B$-decays, but not for mixing. This is because the mixing requires charged to be conserved. 
\end{itemize}

\subsection{Wolfenstein Parametrization}
\begin{itemize}
    \item A first order parametrization of the CKM-matrix.
    \begin{equation}
        V_{\text{WP}} = \begin{pmatrix}
            1 - \frac{1}{2}λ^2 - \frac{λ^{4}}{8} & λ & Aλ^3(\rho - iη) \\
            -λ + A^2λ^{5} \left(1 - 2 (ρ + iη)\right) / 2 & 1 - \frac{1}{2}λ^2 & Aλ^2 \\
            Aλ^3(1 - (1 - λ)(ρ + iη)) & -Aλ^2 + Aλ^{4}(1 - 2(ρ + i η)) / 2 & 1 - A^2λ^4 / 2
        \end{pmatrix}
    \end{equation}
    \item It tells us that $CP$-violation is small in strange and charm sectors, which are dominated by mixing. 
    \item The bottom section have a large $CP$-violation. 
    \item The top quark it is predicted to have a small $CP$-violation. If this is found, it would be a strong indication of new physics.
\end{itemize}
